Effect of quality-adjusted production function inputs

### 2015-04-19 Articles/Presentation_ESEE_2015/ESEE 2015.Rmd
Minor changes.

@@

@@

Note that the contribution of capital (`alpha_1`)
always decreases as energy (`alpha_3`) is allowed to play a role.

@@

>>>>

For now, I've organized the analysis by questions that we would like to answer.

@@

We'll first look at Portugal.

### Portugal

@@

Note that the contribution of capital (`alpha_1`)
always decreases when energy (`alpha_3`) is included as a factor of production.

@@

### United Kingdom
